---
title: \sf AR-IR PRO-seq Analysis Vignette
header-includes:
- \usepackage{color}
- \usepackage{float}
- \DeclareUnicodeCharacter{2212}{-}
output:
  bookdown::html_document2:
    toc: true
fontsize: 14pt
geometry: margin=1in
---


# Readings

Practical Computing for Biologists: Chapters 2, 5, 6, 16, Appendices 2, 3.\

Unix "Basics" and "Finding Things" from UConn CBC: http://bioinformatics.uconn.edu/unix-basics/ \

Software Carpentry Shell Novice lesson: Episodes 5-7:
https://swcarpentry.github.io/shell-novice/

Review basic commands and server access from [UConn_Unix_basics](http://bioinformatics.uconn.edu/unix-basics)

# Last Time:

## Command line navigation:
\
1. Complete path:
```{r engine='bash', eval=F, echo=TRUE}
head /home/username/MEDS5420/lec02_files/the_raven.txt
head /Users/username/MEDS5420/lec02_files/the_raven.txt

```
```{r engine='bash', eval=F, echo=TRUE}
head ~/MEDS5420/lec02_files/the_raven.txt
```
**OR** \
\
2. By using the **relative path** starting from where you are:\

```{r engine='bash', eval=F, echo=TRUE}
head ./username/MEDS5420/lec02_files/the_raven.txt
```
```{r engine='bash', eval=F, echo=TRUE}
head username/MEDS5420/lec02_files/the_raven.txt
```
## Command line utlities so far:

**1.** `pwd` - print working directory\
**2.** `ls` - list directory contents\
**3.** `mkdir` - create a directory\
**4.** `unzip` - decompression\
**5.** `mv` - move file\
**6.** `cp` - copy file\
**7.** `cat` - print contents of file\
**8.** `touch` - create empty file\
**9.** `rm` - remove file\
**10.** `wc` - count lines/words/characters/ in file\
**11.** `>` - redirects output to new file\
**12.** `>>` - redirects output to append to existing file\
**13.** `*` - wildcard that specifies any input\
